---
title: "NSR"
author: "Brian Maitner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NSR R package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Native Species Resolver

The package `NSR` is designed to interact with the Native Species Resolver of the Botanical Information and Ecology Network.  


#Installing NSR
```{r, eval=FALSE}

library(devtools)
install_github("EnquistLab/RNSR/NSR")


```

#The easiest case: one species in one political division

```{r}
library(NSR)
NSR_super_simple(species = "Acer rubrum",
                 country =  "Canada", 
                 state_province = "Ontario")


```

#Multiple species

```{r}

#First, we'll grab some occurrence records from BIEN
library(BIEN)

pima <- BIEN_occurrence_county(country = "United States",state = "Arizona",county = "Pima", all.taxonomy = T,natives.only = F,native.status = T,cultivated = T,political.boundaries = T, limit = 100)

#The NSR function expects 6 columns as input, however only the fields "species" and "country" need to be populated.
#If you ever forget, you can use the function NSR_template as a quick lookup, or to populate.

pima_query<-NSR_template(nrow = nrow(pima))

pima_query$species <- pima$scrubbed_species_binomial
pima_query$country <- pima$country
pima_query$state_province <- pima$state_province
pima_query$county_parish <- pima$county

pima_nsr_results <- NSR(pima_query)

head(pima_nsr_results)

```

#Source metadata
To access metadata for the sources currently consulted by the NSR, use the function `NSR_metadata()`.  To figure out which political divisions contain checklists that were consulted by the NSR, use the function `NSR_political_divisions()`.

```{r}

sources <- NSR_metadata()

checklist_political_divisions <- NSR_political_divisions()

#To only return political division information for a given country, specify that county (or countries) in the field

US_checklists <- NSR_political_divisions(country = "United States")


```


